DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-19 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

\begin{document}

%%%%%%%%% TITLE - PLEASE UPDATE
\title{\LaTeX\ Guidelines for Author Response}  % **** Enter the paper title here

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
\section{Introduction}
We would first like to thank the reviewers for your valuable feedback which helped us to improve the analysis of the proposed method and the overall presentation of the paper. 
Due to space constraints with significant improvement made to the new version of the paper, we would kindly ask reviewers refer the \href{http://www.texample.net/tikz/resources/}{new version of the paper}. we address only the major criticisms below.

\subsection{Common}
\noindent \textbf{1) Unlike stated in the paper, vehicle tracking in images has been studied for years. There are summary papers (e.g. VEHICLE DETECTION AND TRACKING TECHNIQUES: A CONCISE REVIEW Raad Ahmed Hadi1,2 , Ghazali Sulong1 and Loay Edwar George, SIPIJ). There is no mention of prior art.}

\noindent \textbf{Where are comparisons with other activity forecasting/trajectory prediction works?}

\noindent \textbf{I think the authors should reimplement SocialLSTM for 2D data (Stanford UAV dataset seems to be a 2D standard prediction task -- just throw away images and just use the xy plane coordinates, e.g. center of detected bounding box).}
\noindent \textbf{There is no comparison to existing methods, the authors mention that this is due to the lack of existing datasets.}

\noindent \textbf{Who else has experimented on the SYNTHIA dataset? Or are the authors the first ones? Are the authors releasing a specific publicly-available prediction challenge based on SYNTHIA?}
\noindent \textbf{It is not clear if the dataset is released with the paper.}

Currently, experiments on the SYNTHIA dataset~\cite{HernandezBMVC17,ros2016synthia} focus on single frame, static images for semantic labeling or scene representation. To our knowledge, our paper is the first attempt to utilize \textbf{\emph{continuous video streams}} for the prediction problems. We would like to release publicly-available prediction challenge based on Synthia to spur future research upon paper publication.
\subsection{R1}

\noindent \textbf{They adopt fDSST[6] and use it to track detections. What is the novelty, except for the implementation with specific parameters?}

\noindent \textbf{3) 3 very similar LSTMs with different input}

\noindent \textbf{4) The one LSTM with more information performs better. That is not surprising and not a real insight.}

\noindent \textbf{There are a number of inaccuracies}
\noindent \textbf{e.g. line 044, where the authors state that automated driving models are either neural networks or controllers with if-then-else rules}
\noindent \textbf{or line 304, that states that the closest related work to their tracking is an ego-motion regression by Xu,Gao and Darrell}
\noindent \textbf{Line 471 calls Synthia images photo-realistic.}

\noindent \textbf{The actual contributions, and evaluation could be clearer. It took some time to understand the different metrics for detection and tracking as they are supposed to be fused.}

\noindent \textbf{The actual contribution is not significant enough and could be described more clearly.}

@@

\subsection{R2}

\noindent \textbf{SocialLSTM used “Avg. disp. Error”, “Avg. non-linear disp. error” , and “final disp. Error” What was the justification for the metrics the authors chose?}

\noindent \textbf{Line 124 - The authors discuss a "lack of proper metrics for evaluating the temporal prediction result." How are the current metrics poorly suited to the task? What would be better?}

\noindent \textbf{In the SocialLSTM paper’s Related Work section, there are about 20 sources that focus on “Activity forecasting”}

\noindent \textbf{The details about the fusion of “location” and “semantic” information into the LSTM hidden state seemed missing (was a bit vague). A figure of the architecture of the SEG-LSTM would go a long way in clarifying this (or are the authors using Xu et al.'s "End-to-end Learning of Driving Models from Large-scale Video Datasets" FCN-LSTM from Trevor Darrell's group?).}

\noindent \textbf{How is this more than just an engineering pipeline, combining tracking (distilling bounding boxes to coordinates), and then adding an LSTM? SocialLSTM already did the second part in principle.}

\noindent \textbf{I was a bit confused about why the “tracking-by-detection” framework was novel -- how is it different from “Tracking-learning-detection” (TLD),from Z. Kalal, K. Mikolajczyk, and J. Matas. In TPAMI 2012?}

\noindent \textbf{Why are scene semantics privileged (which you also call “auxiliary”) information? If the pipeline relies on fusing the “location” and “semantic” stream, if privileged information is missing at test time, then won’t the pipeline break? (privileged information is usually present at train time, but absent at test time).}

 \noindent \textbf{Can multiple objects be tracked at once, or just one? The video in the supplementary material only showed one object being tracked. What was the average number of objects in each SYNTHIA scene frame?}

 \noindent \textbf{The focus of the paper seems a bit unclear: apparently, the goal is to “predict car’s future odometry given previous egomotion visual input”. But the paper is about prediction of other vehicles’ trajectories, not about predicting one’s own car odometry (which is different).}

\noindent \textbf{I felt like the detection/tracking theme slightly bogs down the main focus of prediction in the paper. I think refocusing it on prediction would strengthen the argument.}

\subsection{R3}
\noindent \textbf{There are too many contributions. For example, I would combine 1 and 3 and maybe also 2 and 4. In general, it is better to have a few strong contributions than many weak ones.}
\noindent \textbf{Section 3 is quite short and it seems that the tracking methodology would fit well here. In general a lot of methodology detail is actually in section 4 (implementation details). Maybe consider reorganizing a little bit.}

\noindent \textbf{In a real car accurate depth information might not be available. Also, tracking and semantic segmentation results in the real world will probably be noisier than for synthetic data. Experiments on real data would make the results much stronger.}

\noindent \textbf{Figure 6: It would be nice to have some state-of-the-art tracking results as reference e.g. ECO, STAPLE CA, SiamFC}

\noindent \textbf{Do you think the results you obtained with the Synthia data will transfer to real-world data?}

\noindent \textbf{Not exactly a request, but maybe something to consider for future work: There are photo-realistic simulators available now (CARLA, Sim4CV, etc.) which allow simulation of autonomous driving with ‘real’ physics and photo-realism similar to Synthia. It would be interesting to implement this system and evaluate ‘real-world’ performance.}

\subsection{Original requirement}
After receiving paper reviews, authors may optionally submit a rebuttal to address the reviewers' comments, which will be limited to a {\bf one page} PDF file.  Please follow the steps and style guidelines outlined below for submitting your author response.

### 2018-01-22 paper/cvpr2018RebuttalKit/egrebuttal_3790.tex

\noindent \textbf{The actual contributions, and evaluation could be clearer. It took some time to understand the different metrics for detection and tracking as they are supposed to be fused.}

\noindent \textbf{The actual contribution is not significant enough and could be described more clearly.}

\subsection{R2}

\noindent \textbf{SocialLSTM used ``Avg. disp. Error", ``Avg. non-linear disp. error" , and ``final disp. Error" What was the justification for the metrics the authors chose?}

\noindent The ``Average displacement error" is

### 2018-01-22 paper/cvpr2018/cvpr2018_3790.tex
paper writing: typos by R3 corrected

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

 Being able to predict other traffic participants' future trajectories is important because it can help to prevent self-driving car from running into other cars. We need to know not just where other cars are, as in the localization case, but also how fast they are moving in order to avoid collisions.
For a human driver, reaction time is a crucial factor that includes recognizing the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake). Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
Therefore, the ability to predict traffic participants' \emph{future} trajectories will greatly benefits the mediated perception approach's driving policy decision making.

@@

Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
In addition, scene parsing results contain quite some spurious information.
Existing methods for scene parsing also mainly focus on static images.
However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by sequence of input frames instead of simply one static frame.
Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicle trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large a mount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community. A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\begin{equation}
J \leftarrow \bm{\mathcal{M}}_p(h, a): H \times A
\label{eq:mapping}
\end{equation}
where the traffic participants $p$ can be of vehicles, cyclists, pedestrians, \emph{etc}. In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on. Historical and future trajectories are defined in a 3D occupancy grid:
\begin{equation}
H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
\label{eq:mapping2}
\end{equation}
where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target (acquired from the depth camera). Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinates $\{x_r,y_r,w_r,h_r\}$ as:
\begin{align}
    x_r = \frac{x}{f}d &, y_r = \frac{y}{f} d  \label{eq:focal_length_1}  \\
    w_r = \frac{w}{f}d &, h_r = \frac{h}{f} d
    \label{eq:focal_length_2}
\end{align}
where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ is as a close approximation.

@@

For predicting vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}. The first two models take sequential 3D occupancy as input. In the third model, we  explore using semantic segmentation as a side ``auxiliary" information to better guide the trajectory prediction.

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 take advantages of scene semantics from  historical frames as auxiliary information $A$. The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information. Semantic inputs are one-hot encoded images with channel number $C$ as the number of semantic category. The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions: $[x, y, w, h, d_{min}, d_{max}]$. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance input dimensions of both trajectory information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.
Note that this model differs from that of~\cite{xu2017end} in that instead of using semantic segmentation as a side task for better directing the learning process of the convnets, SEG-LSTM directly takes scene semantics as input and directs the recurrent net future trajectory prediction. With auxiliary $A$, the trajectory  $j_{t, t+1, \ldots, T}$  to be predicted can be estimated as:

@@

\subsection{Dataset collection}
\begin{algorithm}[h]
\begin{algorithmic}
\caption{\textbf{Car trajectory ground truth collection}}\label{list:dataset_collection}
\STATE \textbf{Step 1} $\rightarrow $ acquiring traffic participants from ground truth annotations with only ``car" as instances.
\STATE \textbf{Step 2} {$\rightarrow $ acquiring frame-based instance information:
{
\bindent
  \IF{POR $> 0.2\%$}
    %\bindent[1.45cm]
    \STATE $\Rightarrow$ start tracking instance;
    \STATE $\Rightarrow$ collecting 3D tracking boundingbox: $[x, y, w, h, d_{min}, d_{max}]$;
    \STATE $\Rightarrow$ collecting semantic labeling image $I_{seg}$;
    \STATE $\Rightarrow$ collecting 2D car pose from RGB input $I_{car}$;
    %\eindent
  \ELSIF{POR $< 0.1\%$}
    \STATE $\Rightarrow$ stop tracking.
    \ENDIF\eindent}
  }
\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with step size 1:
{\bindent
    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input;
  \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
  \eindent}

@@

Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups. The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map. In our experiment, we used only left front camera view data.

The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset. We especially concern about the cars that are relatively close to the driver.
In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
Since depth information is also provided alongside in the SYNTHIA dataset, we back-projecting the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracking vehicle.
Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
We follow the prediction time allocation as in~\cite{xu2017end} that the historical time-span is 3 seconds (corresponds to 15 frames with 5 Hz frame rate in the SYNTHIA dataset).
However, in contrast with~\cite{xu2017end} where only the next 1/3rd of a second is predicted, we strive to predict the next 1.6 second's future trajectory as mentioned previously that it's the reaction time accident reconstruction specialists commonly used~\cite{mcgehee2000driver}.

@@

As it is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small objects, it's very competitive for detecting larger objects. In this paper, we concerns mostly about cars that are close to the driver. Hence, given 0.1\% POR as the the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when objects of interest are large in our problem set.
We also compare the influence of the cut-off threshold for various confident scores and non-maximum suppression (NMS) threshold. It can been seen that both meta-architectures are robust to the cut-off confident scores.
In terms of the effect of NMS cut-off threshold, allowing larger threshold enables the detector to have slightly higher recall, it comes at a cost of multiple redundant overlapping detections and much lower f-score overall. In the following experiment, we adopt SSD with confident score of 0.5 as the cut-off threshold and 0.45 as the default jaccard overlap for NMS.

@@

For the task of sequential prediction, both FtF and FtS share the same base network structure:
a 3-layer recurrent net with 100, 300, 300 LSTM cells.
For SEG-LSTM, since the focus of the scene context is high way driving, auxiliary information is the scene semantics with only ``car" and ``road". The input semantics are one-hot encoded in the dimension of $95\times160\times2$. The CNN for learning high level semantics is composed of four convolutional blocks. Each block includes a convolutional layer, a ReLU activation layer, a maxpooling layer and a dropout layer (as we have observed overfitting during network training). Each convolutional layer has four channels with kernel of size 3.
We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus. DRN achieves 68\% and 82\% pixel mAP on the car and road categories.

>>>>

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict the car's future odometry given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
 We also show the effectiveness of using privileged information (e.g., scene semantics) to further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ {
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream Long Short Term Memory (LSTM)  based network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

 Being able to predict other traffic participants' future trajectories is important because it can help to prevent self-driving car from running into other cars. We need to know not just where other cars are, as in the localization case, but also how fast they are moving in order to avoid collisions.
For a human driver, reaction time is a crucial factor that includes recognizing the light has changed, deciding to continue or brake, and whether to stop engaging the brake (remove foot from accelerator and apply brake). Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
Therefore, the ability to predict traffic participants' \emph{future} trajectories will greatly benefit the mediated perception approach's driving policy decision making.

@@

Nonetheless, vehicles trajectory prediction is a challenging problem: by dissecting visual scene understanding individually (\emph{e.g.,} object detection, semantic segmentation, instance segmentation),  there are still many open challenges for computer vision community.
In addition, the scene parsing results contain quite some spurious information.
Existing methods for scene parsing also mainly focus on static images.
However, autonomous driving is intrinsically a dynamic problem. Human driver makes decision by a sequence of input frames instead of simply one static frame.
Therefore, temporal consistency among continuous frames should also be taken into consideration when designing the interpretable system.

%\textbf{\emph{1.4. Why hasn't it been solved before? (Or, what's wrong with previous proposed solutions? How does mine differ?)}}
Vehicle trajectory prediction is also very related to visual tracking.
In traditional vision based tracking problems (\emph{e.g.},~\cite{wu2013online, wu2015object, mueller2016benchmark}) where target objects go through rather sporadic movements (usually the object trajectory is generated by artificial movement in order to test the robustness of the tracker), the prediction of the target's future trajectory is simply a moot problem.
However, traffic participants generally exhibit regular trajectories (\emph{e.g.,} cars driving on the road, pedestrians walking on the sidewalks). Given law-abiding traffic participants, human drivers subconsciously project visual target's future trajectory.
Nonetheless, due to the missing bridge between traditional visual tracking community and current autonomous driving research community, there is a lack of proper metrics for evaluating the temporal prediction result.

@@

Vision-based semantic segmentation in urban scene is a key functionality for autonomous driving.
%Camvid dataset~\cite{Camvid} consists of a set of monocular images taken in Cambridge UK. However, only 701 images contain pixel-level annotations over a total of 32 categories (combining objects and architectural scenes).
%Similarly, Daimler Urban Segmentation dataset~\cite{scharwachter2013efficient} contains 500 fully labelled monochrome frames for 5 categories.
KITTI benchmark suite~\cite{Geiger2013IJRR} provides a large amount of images of urban scene from Karlsruhe, Germany, with ground truth data for odometry, object detection, tracking, scene flow and stereo benchmarks. However, a limited 430 labelled images are provided for semantic segmentation.
%A common limitation of the aforementioned datasets is the bias introduced by the acquisition of images in a specific city. The LabelMe~\cite{russell2008labelme} project offers the solution by offering around 1,000 fully annotated images of urban environments around the world and more than 3,000 images with partial(noisy) annotations.
More recently, larger projects are constructed:
Cityscapes dataset~\cite{Cordts2016Cityscapes} which consists of a collection of images acquired in 50 cities around Germany, Switzerland and France in difference seasons, and having 5,000 images with fine annotations and 20,000 with coarse annotations over a total of 30 classes. Comma.ai~\cite{santana2016learning} provides 7 and a quarter hours of largely highway driving. Udacity~\cite{udacity} dataset includes 65,000 labels across 9,423 frames at full resolution of $1920\times1200$ at 2Hz.
The use of synthetic data has increased considerably in recent years within computer vision community. A synthetic dataset named SYNTHIA~\cite{mueller2016benchmark} is originally provided for urban scene semantic segmentation generation.
%In~\cite{kaneva2011evaluation}, the authors used a photorealistic virtual world to evaluate the performance of image features under scene changes and image transformations. Synthetic data has also been used for skeleton joints estimation~\cite{shotton2013real}, allowing the classifier invariant to pose, body shape, clothing, etc.
Synthetic dataset has an obvious advantage: a fine annotated image in Cityscape dataset requires on average 1.5 hours which is very labor intensive. Thus, the cost of scaling large project would require a prohibitive economic investment in order to capture images from a larger variety of countries, in different seasons and different traffic conditions.
%For these reasons, a novel synthetic dataset of urban scene called SYNTHIA~\cite{ros2016synthia} is proposed to use synthetic imagery that simulate real urban scenes in a vast variety of conditions and produce the appropriate annotations.
%This dataset is a large collection of images with high variability due to changes in illumination, textures, pose of dynamic objects and camera view-points.

@@

\begin{equation}
J \leftarrow \bm{\mathcal{M}}_p(h, a): H \times A
\label{eq:mapping}
\end{equation}
where the traffic participants $p$ can be vehicles, cyclists, pedestrians, \emph{etc}. In this paper, we focus on vehicle as the sole traffic participant category and ignore the suffix $p$ from now on. Historical and future trajectories are defined in a 3D occupancy grid:
\begin{equation}
H, J \in \Re^{6} =  \{x, y, w, h, d_{min}, d_{max}\}
\label{eq:mapping2}
\end{equation}
where $\{x,y,w,h\}$ define target's 2D boundingbox in image pixel space and $\{d_{min}, d_{max}\}$ define the minimum and maximum relative distance between host car and the tracking target (acquired from the depth camera). Given RGB cameras' focal length $f$, the pixel space 2D boundingbox can be projected into 3D real-world coordinates $\{x_r,y_r,w_r,h_r\}$ as:
\begin{align}
    x_r = \frac{x}{f}d &, y_r = \frac{y}{f} d  \label{eq:focal_length_1}  \\
    w_r = \frac{w}{f}d &, h_r = \frac{h}{f} d
    \label{eq:focal_length_2}
\end{align}
where $d$ is distance between  the center of the camera lens and the center of target. We use the minimum relative distance $d_{min}$ as a close approximation.

@@

For predicting the vehicle's future trajectory, we compare three temporal models based on LSTM cells  as shown in Fig.~\ref{fig:lstm}. The first two models take sequential 3D occupancy as input. In the third model, we  explore using semantic segmentation as a side ``auxiliary" information to better guide the trajectory prediction.

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $A$. The second LSTM layer fuses the outputs from the bottom-most LSTM with the current frames's higher level semantic information. Semantic inputs are one-hot encoded images with channel number $C$ as the number of semantic category. The higher level semantic is extracted from the semantic input through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the historical trajectory.  As described above, the 3D occupancy just has six dimensions: $[x, y, w, h, d_{min}, d_{max}]$. So the bottom-most LSTM not only can learn the temporal information between time-varing trajectory,  but also can balance input dimensions of both trajectory information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.
Note that this model differs from that of~\cite{xu2017end} in that instead of using semantic segmentation as a side task for better directing the learning process of the convnets, SEG-LSTM directly takes scene semantics as input and directs the recurrent net future trajectory prediction. With auxiliary $A$, the trajectory  $j_{t, t+1, \ldots, T}$  to be predicted can be estimated as:

@@

\subsection{Dataset collection}
\begin{algorithm}[h]
\begin{algorithmic}
\caption{\textbf{Car trajectory ground truth collection}}\label{list:dataset_collection}
\STATE \textbf{Step 1} $\rightarrow $ acquiring traffic participants from ground truth annotations with only ``car" as instances.
\STATE \textbf{Step 2} {$\rightarrow $ acquiring frame-based instance information:
{
\bindent
  \IF{POR $> 0.2\%$}
    %\bindent[1.45cm]
    \STATE $\Rightarrow$ start tracking instance;
    \STATE $\Rightarrow$ collecting 3D tracking boundingbox: $[x, y, w, h, d_{min}, d_{max}]$;
    \STATE $\Rightarrow$ collecting semantic labeling image $I_{seg}$;
    \STATE $\Rightarrow$ collecting 2D car pose from RGB input $I_{car}$;
    %\eindent
  \ELSIF{POR $< 0.1\%$}
    \STATE $\Rightarrow$ stop tracking.
    \ENDIF\eindent}
  }
\STATE \textbf{Step 3} $\rightarrow $ splitting sequences into tracklets of 23 frames with stepsize 1:
{\bindent
    \STATE $\Rightarrow$  first 15 frames (5Hz, 3 sec) as training input;
  \STATE $\Rightarrow$  next 8 frames (1.6 sec) as the held-up future trajectory to be predicted.
  \eindent}

@@

Currently, most public datasets with semantic labeling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect a car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
The potential of this virtual world includes extension capabilities: new parts of the cities and road conditions can be easily generated by adding different setups. The major features of the collected dataset include: scene diversity (European style town, modern city, highway and green areas), variety of dynamic objects (cars, pedestrians and cyclists), multiple seasons (dedicated themes for winter, fall, spring and summer), lighting conditions and weather (dynamic lights and shadows, several day-time modes, rain mode and night mode).
There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map. In our experiment, we used only left front camera view data.

The focus of this paper is on car trajectory prediction on highways which corresponds to sequence number 1 in the SYNTHIA dataset. We are especially concerned about the cars that are relatively close to the driver.
In order to decide quantitatively which vehicles are close to the host car, we define pixel occupancy ratio \emph{(POR)} as the ratio between the total number of pixels of the tracking vehicle and the total number of pixels of the camera input.
As in accordance with~\cite{chen2015deepdriving}, we set the reliable car perception as 30 meters so as to guarantee satisfactory control quality when the speed of the host car does not exceed 72km/h.
Since depth information is also provided alongside in the SYNTHIA dataset, we back-project the segmented instance region onto the depth maps and estimate that the POR of 0.2\% and 0.1\% correspond to roughly 30 meters and 100 meters of relative distance between the host car and the tracked vehicle.
Hence, we start tracking the target when the POR of the detected vehicle is larger than 0.2\%  so as to suffice the safety distance for driver to make timely reaction and stop tracking the vehicle when the POR is smaller than 0.1\% indicating the target car is too far to influence driving policy.
We follow the prediction time allocation as in~\cite{xu2017end} that the historical time-span is 3 seconds (corresponds to 15 frames with 5 Hz frame rate in the SYNTHIA dataset).
However, in contrast with~\cite{xu2017end} where only the next 1/3rd of a second is predicted, we strive to predict the next 1.6 second's future trajectory as mentioned previously that it's the reaction time accident reconstruction specialists commonly used~\cite{mcgehee2000driver}.

@@

As is also pointed out in the paper~\cite{huang2017speed} that SSD, albeit is less advantageous in detecting small objects, it's very competitive for detecting larger objects. In this paper, we are mostly concerned about cars that are close to the driver. Hence, given 0.1\% POR as the the cut-off threshold, the presented problem favors detectors that are robust in detecting larger objects.
Tab.~\ref{tab:ssd_fasterrcnn} also verifies that SSD is indeed more competitive when objects of interest are large in our problem set.
We also compare the influence of the cut-off threshold for various confident scores and non-maximum suppression (NMS) threshold. It can been seen that both meta-architectures are robust to the cut-off confident scores.
In terms of the effect of NMS cut-off threshold, allowing larger threshold enables the detector to have slightly higher recall, it comes at a cost of multiple redundant overlapping detections and much lower f-score overall. In the following experiment, we adopt SSD with confident score of 0.5 as the cut-off threshold and 0.45 as the default jaccard overlap for NMS.

@@

For the task of sequential prediction, both FtF and FtS share the same base network structure:
a 3-layer recurrent net with 100, 300, 300 LSTM cells.
For SEG-LSTM, since the focus of the scene context is high-way driving, auxiliary information is the scene semantics with only ``car" and ``road". The input semantics are one-hot encoded in the dimension of $95\times160\times2$. The CNN for learning high level semantics is composed of four convolutional blocks. Each block includes a convolutional layer, a ReLU activation layer, a maxpooling layer and a dropout layer (as we have observed overfitting during network training). Each convolutional layer has four channels with kernel of size 3.
We adopt the state-of-the-art semantic segmentation networks: Dilated Residual Networks (DRN)~\cite{yu2017dilated} and retrain on the SYNTHIA corpus. DRN achieves 68\% and 82\% pixel mAP on the car and road categories.
